---
title: "***England report***"
output:
  html_document:
    theme: cerulean
params:
  month: 4
  year: 2019
  executor: "Cristina Muschitiello"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set-up options fixed globally in the Rmd (R lines not included as default). 

library(data.table)
library(EQL)
library(ggthemes)
library(kdensity)
library(magrittr)
library(PrescRiptions)
library(reactable)
library(tidyverse)
options(scipen = 999)
ggplot2::theme_set(ggthemes::theme_economist()) # Sets graphs themes to "The Economist" style

monthNames = c("January", "February", "March", "April", "May", "June", "July",
               "August","September", "October", "November","December") # Object to recall all months names 
  
NameMonth = monthNames[as.numeric(params$month)] # Months resulting from parameter

settings = PrescRiptions::setConfig(rootdir = "/cloud/project/output",
                                    year = params$year, month = params$month, region = "England") # Configuration option defined in the Prescriptions package. This line specifies where to save the output automatically downloaded from the package (rootdir), and provides parameters for year, month and region.

dataAll = PrescRiptions::monthlyData_import(settings, sample = TRUE) # Imports data from repo and website

for (i in 1:length(dataAll)){
  print(names(dataAll)[i])
  assign(names(dataAll)[i],dataAll[[i]])
} # Assigns names to data.tables

# dirs = dirsGen(settings)

practiceBridge = PrescRiptions::plpdDemogBridge(get(settings$plpdName), get(settings$demogMapName)) # Provides a mapping for practice names across different data sources


```

## England report `r paste(NameMonth, params$year, sep = " ")`

This report is generated using information on a **sample** of drugs prescriptions in primary care in *England* for the month `r paste(NameMonth, params$year, sep = " ")`. 

The report is parametrized using parameters reported in the **YAML** section of the Rmd and executed by *`r params$executor`*.

<span style="background-color:#ffff66">You can change *month*, *year* and *executor* name of the present report</span>, by changing the values of the corresponding `params` in the **YAML** section.

---

## Data description

The dataset used for this report are obtained from **NHS** Presentation Level prescription data. This dataset provides information on **all individual prescription** of **drugs and appliances** provided in **primary care** in *England*

The dataset is quite rich, with monthly data running from sept. 2011. Each month is about 1.5Gb. For a sample period (2018 and 2019) this dataset is made available using the **PrescRiptions** package which will be introduced in later sections.

Because running test on such large dataset might cause problems, the package allow for the usage of complete data or *sample* data.
The present report is produced on a sample of 500.000 data rows from the complete dataset.

The type of information included in the data are:

```{r echo=TRUE}

head(get(settings$plpdName))

```

## Summary stats

The following table provides a summary of key quantitative information for the month selected (`r paste(monthNames, params$year, sep = " ")`)

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt <- get(settings$plpdName) %>%
  select(PRACTICE, ITEMS, NIC, ACT.COST, QUANTITY) # Selects only relevant variables
dt_stat <- data.table(sapply(dt[,c(2:5)], summary), keep.rownames = TRUE) # Provides summary information for relevant variables

reactable(dt_stat)

```

## Cost Distribution

We check the distribution of Net Ingredient Costs aggregated across practices

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_NIC = dt %>%
  select(NIC, PRACTICE) %>%
  group_by(PRACTICE) %>% 
  summarise(tot_NIC = sum(NIC)) %>%
  as.data.frame()
# Computes NEt Ingrendient Costs Aggregated at Practice level

dt_NIC %>%
  ggplot(aes(x=tot_NIC)) +
  geom_density(fill="#E95420", color="#E95420", alpha=0.8) + 
  xlim(0, 350000)+
  labs(title=paste0("Net Ingrent Cost (NIC) - Distribution by Practice"),
  subtitle = paste0("England - ",NameMonth," ", params$year),
       caption="source: NHS",
       x="NIC",y="Density") + 
  theme(plot.title = element_text(color="#333333"))+
  scale_x_continuous(labels = function(x) stringr::str_wrap(x, width = 20))+
   # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,vjust=0.4, hjust=0.5,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
# Creates a graphical representation of the NIC paid by single practices


```

## Prescription rates

We now check how do NIC vary when considering total costs as a rate, that is when we divide total costs by the total number of registered patients in the practice.

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_demog_clean <- get(settings$demogName)  %>% 
  filter(ORG_TYPE == "GP" & AGE_GROUP_5 == "ALL" & SEX == "ALL") %>%
  select(PRACTICE = ORG_CODE,  NUMBER_OF_PATIENTS)
# Selects a clean version of population data

dt_NIC_rate <- left_join(dt_NIC, dt_demog_clean, by = "PRACTICE") %>%
  drop_na()
# Remove observations with empty population data

dropped_practices <- nrow(dt_NIC)-nrow(dt_NIC_rate)
# stores the number of dropped practices

dt_NIC_rate$NIC_rate <- (dt_NIC_rate$tot_NIC / dt_NIC_rate$NUMBER_OF_PATIENTS)*100 # Creates a rate variable

dt_NIC_rate %>%
  ggplot(aes(x=NIC_rate)) +
  geom_density(fill="#E95420", color="#E95420", alpha=0.8) + 
  xlim(0, 3000)+
  labs(title=paste0("Net Ingrent Cost (NIC) per capita - Distribution by Practice"),
  subtitle = paste0("England - ",NameMonth," ", params$year),
       caption="source: NHS",
       x="NIC per capita",y="Density") + 
  theme(plot.title = element_text(color="#333333"))+
  # scale_x_continuous(labels = function(x) stringr::str_wrap(x, width = 20))+
   # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,vjust=0.4, hjust=0.5,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
# Provides a graphical representation of Net Ingredient Costs per capita

```

The figure above uses Net Ingredient Costs (NIC) computed as a rate per capita. The distribution looks much clearer now!

## High NIC per capita practices

We now identify practices with high Net Ingredient Costs (NIC) per patient. For simplicity, we select as high-prescribing those practices who are in the top 5% for the NIC per capita.

```{r echo=FALSE, warning=FALSE, message = FALSE}

n <- 5
dt_NIC_rate_top5 <- dt_NIC_rate[dt_NIC_rate$NIC_rate > quantile(dt_NIC_rate$NIC_rate,prob=1-n/100),] #Identifies practices in the top 5% quantile in terms of cost per capita

reactable(dt_NIC_rate_top5)

```

The table above indicates basic information of high-NIC per capita practices.
