---
title: "**Practice reports**"
output:
  html_document:
    theme: cerulean
params:
  month: "05"
  year: 2019
  gp: "A81005"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(EQL)
library(ggthemes)
library(kdensity)
library(magrittr)
library(PrescRiptions)
library(reactable)
library(tidyverse)
options(scipen = 999)
ggplot2::theme_set(ggthemes::theme_economist()) # Sets graphs themes to "The Economist" style

monthNames = c("January", "February", "March", "April", "May", "June", "July",
               "August","September", "October", "November","December")   # Object to recall all months names 
  
NameMonth = monthNames[as.numeric(params$month)]# Months resulting from parameter

settings = PrescRiptions::setConfig(rootdir = "/cloud/project/output",
                                    year = params$year, month = params$month, region = "England")# Configuration option defined in the Prescriptions package. This line specifies where to save the output automatically downloaded from the package (rootdir), and provides parameters for year, month and region.

dataAll = PrescRiptions::monthlyData_import(settings, sample = TRUE)# Imports data from repo and website

for (i in 1:length(dataAll)){
  print(names(dataAll)[i])
  assign(names(dataAll)[i],dataAll[[i]])
}# Assigns names to data.tables

practiceBridge = PrescRiptions::plpdDemogBridge(get(settings$plpdName), get(settings$demogMapName))# Provides a mapping for practice names across different data sources

dt <- get(settings$plpdName) %>%
  select(PRACTICE, ITEMS, NIC, ACT.COST, QUANTITY) # Selects only relevant variables
dt_stat <- data.table(sapply(dt[,c(2:5)], summary), keep.rownames = TRUE) # Provides summary information for relevant variables



```


## **Report for month `r NameMonth` of `r params$year` and for the following GP: `r params$gp`**

This report is generated using information on a **sample** of drugs prescriptions in primary care in *England* for the month `r paste(NameMonth, params$year, sep = " ")`.

The report is parametrized using parameters reported in the **YAML** section of the Rmd and executed by *`r params$executor`*.

<span style="background-color:#ffff66">You can change *month*, *year* and *Practice* name (gp) of the present report</span>, by changing the values of the corresponding `params` in the **YAML** section.

If you don't know which GP to chise, pick up one in following list showing a sample of 100 GPs included in the data-sample:

```{r echo=FALSE}

sample(dt[,unique(PRACTICE)],100)

```

---

## Summary stats

The practice presents the following values:

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_Practices = dt %>%
  select(ITEMS, NIC, ACT.COST, QUANTITY, PRACTICE) %>%
  group_by(PRACTICE) %>% 
  summarise(tot_ITEMS = sum(ITEMS), tot_NIC = sum(NIC)) %>%
  as.data.frame()
# Compute total by practice

dt_GP <- dt_Practices %>%
  filter(PRACTICE == params$gp) # Selects information for the practice specified in the YAML section

```

- `r dt_GP$tot_ITEMS` prescribed items
- `r dt_GP$tot_NIC` Net Ingredient Costs (NIC)

## Cost Distribution

We check how the practice performs in terms of costs compared to all other practices.

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_NIC = dt %>%
  select(NIC, PRACTICE) %>%
  group_by(PRACTICE) %>% 
  summarise(tot_NIC = sum(NIC)) %>%
  as.data.frame()
# Computes Net Ingrendient Costs Aggregated at Practice level

dt_NIC_GP = dt %>%
  select(NIC, PRACTICE) %>%
  group_by(PRACTICE) %>% 
  summarise(tot_NIC = sum(NIC)) %>%
  filter(PRACTICE == params$gp) %>%
  as.data.frame() # Computes total NIC for the practice specified in the YAML section

dt_NIC %>%
  ggplot(aes(x=tot_NIC)) +
  geom_density(fill="#E95420", color="#E95420", alpha=0.8) + 
  xlim(0, 350000)+
  labs(title=paste0("Net Ingrent Cost (NIC) - Distribution by Practice"),
  subtitle = paste0("England - ",NameMonth," ", params$year),
       caption="source: NHS",
       x="NIC",y="Density") + 
  geom_vline(xintercept=dt_NIC_GP$tot_NIC, colour = "deepskyblue") +
  theme(plot.title = element_text(color="#333333"))+
  scale_x_continuous(labels = function(x) stringr::str_wrap(x, width = 20))+
   # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,vjust=0.4, hjust=0.5,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
# Plots the distribution of the NIC by practice, including the one of the specified practice in the YAML (as a vertical line)

```

The figure above shows the value of the selected practice (in light blue).

The practice `r params$gp` has a NIC which is in the top `r round(length(which(dt_GP$tot_NIC> dt_NIC$tot_NIC))/nrow(dt_NIC),2) *100` of the NIC distribution.

## Prescription rates

We now report the prescription rate for the selected practice.

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_demog_clean <-  get(settings$demogName)  %>% 
  filter(ORG_TYPE == "GP" & AGE_GROUP_5 == "ALL" & SEX == "ALL") %>%
  select(PRACTICE = ORG_CODE,  NUMBER_OF_PATIENTS)
# Selects a clean version of population data

dt_NIC_rate <- left_join(dt_NIC, dt_demog_clean, by = "PRACTICE") %>%
  drop_na()
# Remove observations with empty population data

dropped_practices <- nrow(dt_NIC)-nrow(dt_NIC_rate)
# stores the number of dropped practices

dt_NIC_rate$NIC_rate <- (dt_NIC_rate$tot_NIC / dt_NIC_rate$NUMBER_OF_PATIENTS)*100 # Creates a rate variable

dt_NIC_rate_gp <- dt_NIC_rate %>%
  filter(PRACTICE == params$gp) # Computes the prescription rate of the practice specified in the YAML section

dt_NIC_rate %>%
  ggplot(aes(x=NIC_rate)) +
  geom_density(fill="#E95420", color="#E95420", alpha=0.8) + 
  xlim(0, 3000)+
  labs(title=paste0("Net Ingrent Cost (NIC) per capita- Distribution by Practice"),
  subtitle = paste0("England - ",NameMonth," ", params$year, " - GP: ",params$gp),
       caption="source: NHS",
       x="NIC per capita",y="Density") + 
  geom_vline(xintercept=dt_NIC_rate_gp$NIC_rate, colour = "deepskyblue") +
  theme(plot.title = element_text(color="#333333"))+
  # scale_x_continuous(labels = function(x) stringr::str_wrap(x, width = 20))+
   # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,vjust=0.4, hjust=0.5,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
# Plots the NIC per capita across all practices, with the selected practice NIC per capita reported as a vertical line

```

The figure above shows the value of the Net Ingredient Costs (NIC) per capita of the selected practice (in light blue).

The practice `r params$gp` has a NIC which is in the top `r round(length(which(dt_NIC_rate_gp$NIC_rate> dt_NIC_rate$NIC_rate))/nrow(dt_NIC_rate),2) *100` of the NIC distribution.

## Highly prescribing practices

```{r echo=FALSE, warning=FALSE, message = FALSE}

n <- 5
dt_NIC_rate_top5 <- dt_NIC_rate[dt_NIC_rate$NIC_rate > quantile(dt_NIC_rate$NIC_rate,prob=1-n/100),] # Identifies top prescribing practices

```

The practice **`r if(params$gp %in% dt_NIC_rate_top5$PRACTICE) {"is"} else {"is not"}`** one of the top prescribing practices.

