---
title: "***High Prescribing GPs report***"
output:
  html_document:
    theme: cerulean
params:
  month: "07"
  year: 2019
  threshold: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(EQL)
library(ggthemes)
library(kdensity)
library(magrittr)
library(PrescRiptions)
library(reactable)
library(tidyverse)
options(scipen = 999)
ggplot2::theme_set(ggthemes::theme_economist()) # Sets graphs themes to "The Economist" style

monthNames = c("January", "February", "March", "April", "May", "June", "July",
               "August","September", "October", "November","December")   # Object to recall all months names 
  
NameMonth = monthNames[as.numeric(params$month)]# Months resulting from parameter

settings = PrescRiptions::setConfig(rootdir = "/cloud/project/output",
                                    year = params$year, month = params$month, region = "England")# Configuration option defined in the Prescriptions package. This line specifies where to save the output automatically downloaded from the package (rootdir), and provides parameters for year, month and region.

dataAll = PrescRiptions::monthlyData_import(settings, sample = TRUE)# Imports data from repo and website

for (i in 1:length(dataAll)){
  print(names(dataAll)[i])
  assign(names(dataAll)[i],dataAll[[i]])
}# Assigns names to data.tables

practiceBridge = PrescRiptions::plpdDemogBridge(get(settings$plpdName), get(settings$demogMapName))# Provides a mapping for practice names across different data sources

dt <- get(settings$plpdName) %>%
  select(PRACTICE, ITEMS, NIC, ACT.COST, QUANTITY)  # Selects only relevant variables

dt_stat <- data.table(sapply(dt[,c(2:5)], summary), keep.rownames = TRUE)# Provides summary information for relevant variables

dt_Practices = dt %>%
  select(ITEMS, NIC, ACT.COST, QUANTITY, PRACTICE) %>%
  group_by(PRACTICE) %>% 
  summarise(tot_ITEMS = sum(ITEMS), tot_NIC = sum(NIC)) %>%
  as.data.frame()
# Compute total by practice

dt_NIC = dt %>%
  select(NIC, PRACTICE) %>%
  group_by(PRACTICE) %>% 
  summarise(tot_NIC = sum(NIC)) %>%
  as.data.frame()
# Computes Net Ingrendient Costs Aggregated at Practice level

dt_demog_clean <- get(settings$demogName)  %>% 
  filter(ORG_TYPE == "GP" & AGE_GROUP_5 == "ALL" & SEX == "ALL") %>%
  select(PRACTICE = ORG_CODE,  NUMBER_OF_PATIENTS)
# Selects a clean version of population data

dt_NIC_rate <- left_join(dt_NIC, dt_demog_clean, by = "PRACTICE") %>%
  drop_na()
# Remove observations with empty population data

dropped_practices <- nrow(dt_NIC)-nrow(dt_NIC_rate)
# stores the number of dropped practices

dt_NIC_rate$NIC_rate <- (dt_NIC_rate$tot_NIC / dt_NIC_rate$NUMBER_OF_PATIENTS)*100 # Creates a rate variable

n <- params$threshold # Recalls the parameter variable for thoreshold
dt_NIC_rate_top5 <- dt_NIC_rate[dt_NIC_rate$NIC_rate > quantile(dt_NIC_rate$NIC_rate,prob=1-n/100),] # Identifies high-cost practices 

```

## *Report for month `r NameMonth` of `r params$year` and for the high prescribing practices*

This report is generated using information on a **sample** of drugs prescriptions in primary care in *England* for the month `r paste(NameMonth, params$year, sep = " ")`.

The report is parametrized using parameters reported in the **YAML** section of the Rmd and executed by *`r params$executor`*.</span>

*High prescribing Practices* are defined as those practices which are in a top percentage of Net Ingredient Costs (NIC) per capita.
In this example the threshold chosen is ***`r params$threshold`***.

<span style="background-color:#ffff66">In this report you can change *month*, *year* and *Threshold*</span>, by changing the values of the corresponding `params` in the **YAML** section.

---

## Summary stats

The following table contains prescription information on high prescribing practices.

```{r echo=FALSE, warning=FALSE, message = FALSE}

reactable(dt_NIC_rate_top5)

```

## Cost Distribution

In this section we provide a graphical distribution of Net Ingredient Costs (NIC) of high-cost practices

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_NIC_rate_top5 %>%
  ggplot(aes(x=tot_NIC)) + 
  geom_histogram(fill="#E95420", color="#E95420") +
  labs(title=paste0("Net Ingrent Cost (NIC) - High Cost Practices"),
  subtitle = paste0("England - ",NameMonth," ", params$year),
       caption="source: NHS",
       x="NIC",y="Density") + 
  theme(plot.title = element_text(color="#333333"))+
  # scale_x_continuous(labels = function(x) stringr::str_wrap(x, width = 20))+
   # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,vjust=0.4, hjust=0.5,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
# Represents Net Ingredient Costs distribution for high-prescribing practices

```

## Prescription rates

We now report NIC per capita for high-cost practices

```{r echo=FALSE, warning=FALSE, message = FALSE}

dt_NIC_rate_top5_b <- dt_NIC_rate_top5 %>% filter(dt_NIC_rate_top5$NUMBER_OF_PATIENTS >10)
# I remove an outlier among practices shortlisting practices with more than 10 patients only

dt_NIC_rate_top5_b %>%
  ggplot(aes(x=NIC_rate)) + 
  geom_histogram(fill="#E95420", color="#E95420") +
  labs(title=paste0("Net Ingrent Cost (NIC) per capita - High Cost Practices"),
  subtitle = paste0("England - ",NameMonth," ", params$year),
       caption="source: NHS",
       x="NIC per capita",y="Density") + 
  theme(plot.title = element_text(color="#333333"))+
  # scale_x_continuous(labels = function(x) stringr::str_wrap(x, width = 20))+
   # scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
  theme(axis.text.x = element_text(size=9,vjust=0.4, hjust=0.5,color="#333333"))+
  theme(axis.text.y = element_text(size=9,vjust=0.4, hjust=1,color="#333333"))+
  theme(axis.title.x = element_text(margin=margin(10,10,0,0),color="#333333"))+
  theme(axis.title.y = element_text(margin=margin(10,10,10,0),color="#333333"))
# Reports NIC distribution per capita for high-cost practices only

```

